An investigation of the clinical utility of preoperative cardiopulmonary exercise testing in patients undergoing major pancreatic surgery.

### 2016-02-13 Presentations/viva_presentation_short.tex
Viva Presentation - Rename all sections - Move case study to end of presentation - Next - start cutting slides
Viva Presentation - Short
- TexStudio crashed for the first time today!!!!

%------------------------------------------------
\section{Introduction}
\subsection{Pancreatic cancer}
\begin{frame}
	\frametitle{Pancreatic cancer} %Epidemiology/outcomes
	\begin{block}{The Problem}
		\begin{itemize}
			\item 10th common but 5th common cause of cancer death
			\item Survival	1-yr: 20.8\%, 5-yr: 3.3\%, 10yr: 1.1\%
			\item Operable disease : approx 15\%
		\end{itemize}
	\end{block}
	\begin{block}{Treatment}
		\begin{itemize}
			\item Surgery + adjuvant chemotherapy only chance of cure
		\end{itemize}
	\end{block}
	\begin{block}{Pancreaticoduodenectomy}
		\begin{itemize}
			\item Complex surgery with 50\% morbidity
			\item Performed only in specialist centres
			\item Patient fitness is as important as tumour factors
		\end{itemize}
	\end{block}
\end{frame}

@@

\subsection{CPET}
\begin{frame}
	\frametitle{Risk Stratification }
	\framesubtitle{Section 1.4 Pages 13-18 }
	\begin{itemize}
		\item Patient fitness is important determinant of outcome
		\item Effect of comorbidity on function is difficult to assess
		\item POSSUM, APACHE, mGPS, E-PASS, etc.
		\item Static measures do not predict performance under stress
		\item Do not provide targets for prehabilitation
		\item Pancreas specific risk factors of POPF
		\begin{itemize}
			\item Soft pancreas
			\item Narrow pancreatic duct
			\item Pathology not obstructing PD
			\item These factors are not modifiable
			\item Coronary artery disease! (Lin 2004)
		\end{itemize}
	\end{itemize}
\end{frame}

@@

\section{Methods}
\begin{frame}
	\frametitle{Patients and Methods}
	\begin{itemize}
		\item Patients undergoing pancreaticoduodenectomy at Glasgow Royal Infirmary
		\item August 2008 - August 2012
		\item Prospectively maintained MS Access database
		\item Preoperative data - Bloods, co-morbidity including POSSUM Physiology Score, stent information
		\item Cardiopulmonary exercise testing
		\item Prospective recording of complications using ISGPS or Clavie-Dindo classification
		\item Serial measurements of biochemical parameters during first postoperative week
	\end{itemize}
\end{frame}

%--CHAPTER 2----CHAPTER 2----CHAPTER 2----CHAPTER 2----CHAPTER 2----CHAPTER 2----CHAPTER 2--
\section{Chapter 2}
\begin{frame}
	\frametitle{CPET and Postoperative Outcomes}
	\framesubtitle{Chapter 2 Page 56; (n=100)}
	\begin{block}{\textbf{Complications}}
		Low $\dot{V}_{O_2}$AT associated with pancreatic fistula (16\% vs 35\%) \\
		Not associated with cardio-respiratory complications or mortality
	\end{block}

@@

\begin{frame}
	\frametitle{CPET and Postoperative Outcomes}
	\framesubtitle{The Glasgow Cohort}
	\begin{figure}
		\centering
		\includegraphics[height=0.35\textheight]{../Figures/cpet_outcomes_dist_of_AT}
	\end{figure}

@@

\begin{frame}
	\frametitle{CPET and Postoperative Outcomes}
	\framesubtitle{Citations}
	\begin{columns}[c]
	\column{0.4\textwidth}
		\begin{figure}
			\centering
			\includegraphics[width=\textwidth]{cpet_citations}
		\end{figure}

	\column{0.6\textwidth}
	Why is $\dot{V}_{O_2}$AT so low in patients undergoing pancreatic surgery?\\
	\medskip
	What factors are associated with a low $\dot{V}_{O_2}$AT?\\
	\medskip
	Why was $\dot{V}_{O_2}$AT not associated with cardio-respiratory complications?\\
	\medskip
	Does $\dot{V}_{O_2}$AT truely reflect cardiopulmonary function in this cohort of patients?\\	
	\end{columns}
\end{frame}

%--CHAPTER 3----CHAPTER 3----CHAPTER 3----CHAPTER 3----CHAPTER 3----CHAPTER 3----CHAPTER 3--
\section{Chapter 3}

\begin{frame}
	\frametitle{Chapter 3}
	\framesubtitle{CPET, Jaundice and Preoperative Pathophysiology - Page 76-96 }
	\begin{block}{Title}
	An investigation into the relationship between cardiopulmonary exercise testing, preoperative pathophysiology and obstructive jaundice in patients undergoing pancreaticoduodenectomy.
	\end{block}
\end{frame}

\begin{frame}
	\frametitle{Distribution of Jaundice in the study cohort }
	\framesubtitle{n=138}

	\begin{figure}
		\centering
		\includegraphics[width=0.7\linewidth]{jaundice_distribution}
		\caption{}
		\label{fig:jaundice_distribution}
	\end{figure}
\end{frame}

\begin{frame}
	\frametitle{Jaundice and patient characteristics}
	\framesubtitle{Table 3.1 Page 83, Table 3.2 Page 85 }
	\begin{figure}
		\includegraphics[height=0.4\textheight]{jaundice_vs_patient_factors}
	\end{figure}
	{\scriptsize			
	Severity of systemic inflammation proportionate to severity of jaundice. \\
	\medskip

@@

	Jaundiced patients were more likely to be anaemic (p$<$0.001) with lower haematocrit (p$<$0.001) and lower mean corpuscular volume (p=0.001).\\
	\medskip

	No significant difference in the preoperative renal function, prothrombin time and white cell count between jaundiced and non-jaundiced patients.\\
	}
\end{frame}

\begin{frame}
	\frametitle{CPET and Jaundice}
	\framesubtitle{Figure 3.1 Page 87}
	\begin{columns}[t]
		\column{0.5\textwidth}
			\begin{figure}
				\centering
				\includegraphics[width=\textwidth]{../Figures/cpet_oj_scatter_at_bil}
				\caption{$\dot{V}_{O_2}$AT versus serum bilirubin}
				\label{fig:cpet_oj_scatter_at_bil}
			\end{figure}

		\column{0.5\textwidth}
			\begin{figure}
				\includegraphics[width=\textwidth]{../Figures/cpet_oj_scatter_peak_bil}
				\caption{$\dot{V}_{O_2}$Peak versus serum bilirubin}
				\label{fig:cpet_oj_scatter_peak_bil}
			\end{figure}
	\end{columns}
\end{frame}

\begin{frame}
	\frametitle{$\dot{V}_{O_2}$ vs Patient Factors }
	\framesubtitle{Table 3.6 Page 91 - Multivariate binary logistic regression}

	Factors associated with $\dot{V}_{O_2}$AT $<$ 10 ml/kg/min
	\begin{table}
		\begin{tabular}{l l l l}
			           & HR   & 95\% CI    & p     \\ \hline
			Female sex & 3.75 & 1.57-8.95  & 0.003 \\
			BMI$>$25   & 3.65 & 1.61-8.26  & 0.002 \\
			Cancer     & 4.02 & 1.33-12.16 & 0.014 \\
			CRP$>$10   & 2.98 & 1.29-6.86  & 0.010
		\end{tabular}
	\end{table}

%--CHAPTER 4----CHAPTER 4----CHAPTER 4----CHAPTER 4----CHAPTER 4----CHAPTER 4----CHAPTER 4--
\section{Chapter 4}

@@

\section{Chapter 5}

@@

\section{Chapter 6}
\begin{frame}
	\frametitle{Chapter 6}
	\framesubtitle{Postoperative CRP and complications}
	\begin{block}{Title}
		An investigation into the relationship between postoperative systemic inflammation and complications after pancreaticoduodenectomy.
	\end{block}
\end{frame}

@@

>>>>

%------------------------------------------------
%\section{Chapter 1/ Introduction}
\section[Chapter 1]{Introduction}

\begin{frame}
	\frametitle{Pancreatic cancer} %Epidemiology/outcomes
	\begin{block}{The Problem}
		\begin{itemize}
			\item 10th common but 5th common cause of cancer death
			\item Survival	1-yr: 20.8\%, 5-yr: 3.3\%, 10yr: 1.1\%
			\item Operable disease : approx 15\%
		\end{itemize}
	\end{block}
	\begin{block}{Treatment}
		\begin{itemize}
			\item Surgery + adjuvant chemotherapy only chance of cure
		\end{itemize}
	\end{block}
	\begin{block}{Pancreaticoduodenectomy}
		\begin{itemize}
			\item Complex surgery with 50\% morbidity
			\item Performed only in specialist centres
			\item Patient fitness is as important as tumour factors
		\end{itemize}
	\end{block}
\end{frame}

@@

\begin{frame}
	\frametitle{Risk Stratification }
	\framesubtitle{Section 1.4 Pages 13-18 }
	\begin{itemize}
		\item Patient fitness is important determinant of outcome
		\item Effect of comorbidity on function is difficult to assess
		\item POSSUM, APACHE, mGPS, E-PASS, etc.
		\item Static measures do not predict performance under stress
		\item Do not provide targets for prehabilitation
		\item Pancreas specific risk factors of POPF
		\begin{itemize}
			\item Soft pancreas
			\item Narrow pancreatic duct
			\item Pathology not obstructing PD
			\item These factors are not modifiable
			\item Coronary artery disease! (Lin 2004)
		\end{itemize}
	\end{itemize}
\end{frame}

@@

\begin{frame}
	\frametitle{Patients and Methods}
	\begin{itemize}
		\item Patients undergoing pancreaticoduodenectomy at Glasgow Royal Infirmary
		\item August 2008 - August 2012
		\item Prospectively maintained MS Access database
		\item Preoperative data - Bloods, co-morbidity including POSSUM Physiology Score, stent information
		\item Cardiopulmonary exercise testing
		\item Prospective recording of complications using ISGPS or Clavie-Dindo classification
		\item Serial measurements of biochemical parameters during first postoperative week
	\end{itemize}
\end{frame}

%--CHAPTER 2----CHAPTER 2----CHAPTER 2----CHAPTER 2----CHAPTER 2----CHAPTER 2----CHAPTER 2--
\section[Chapter 2]{CPET and Postoperative Outcomes}
\begin{frame}
	\frametitle{CPET and Postoperative Outcomes}
	\framesubtitle{Does CPET have a role in risk stratification of patients?}
	\begin{block}{\textbf{Complications}}
		Low $\dot{V}_{O_2}$AT associated with pancreatic fistula (16\% vs 35\%) \\
		Not associated with cardio-respiratory complications or mortality
	\end{block}

@@

\begin{frame}
	\frametitle{CPET in the Glasgow Cohort}
	\framesubtitle{Why was 'aerobic capacity' so poor in these patients yet outcomes were comparable?}
	\begin{figure}
		\centering
		\includegraphics[height=0.35\textheight]{../Figures/cpet_outcomes_dist_of_AT}
	\end{figure}

@@

\begin{frame}
	\frametitle{CPET and Postoperative Outcomes}
	\framesubtitle{Publication, Citations and more questions!}

	\begin{figure}
		\includegraphics[width=0.6\linewidth]{cpet_hpb_publication}
	\end{figure}

	\begin{columns}[c]
		\column{0.4\textwidth}
			\begin{figure}
				\includegraphics[width=0.6\textwidth]{cpet_citations}
			\end{figure}

		\column{0.6\textwidth}
			{\footnotesize 	Why is $\dot{V}_{O_2}$AT so low in patients undergoing pancreatic surgery?\\
				\medskip
				What factors are associated with a low $\dot{V}_{O_2}$AT?\\
				\medskip
				Why was $\dot{V}_{O_2}$AT not associated with cardio-respiratory complications?\\
				\medskip
				Does $\dot{V}_{O_2}$AT truly reflect cardiopulmonary function in this cohort of patients?\\	
			}

	\end{columns}
\end{frame}

%--CHAPTER 3----CHAPTER 3----CHAPTER 3----CHAPTER 3----CHAPTER 3----CHAPTER 3----CHAPTER 3--
\section[Chapter 3]{CPET, Jaundice and Preoperative Pathophysiology}

\begin{frame}
	\frametitle{CPET, Jaundice and Preoperative Pathophysiology}
	\framesubtitle{What were the preoperative patient factors that were associated with a low $\dot{V}_{O_2}$?}
	Factors associated with $\dot{V}_{O_2}$AT $<$ 10 ml/kg/min
	\begin{table}
		\begin{tabular}{l l l l}
			& HR   & 95\% CI    & p     \\ \hline
			Female sex & 3.75 & 1.57-8.95  & 0.003 \\
			BMI$>$25   & 3.65 & 1.61-8.26  & 0.002 \\
			Cancer     & 4.02 & 1.33-12.16 & 0.014 \\
			CRP$>$10   & 2.98 & 1.29-6.86  & 0.010
		\end{tabular}
	\end{table}

\begin{frame}
	\frametitle{What was the effect of jaundice on $\dot{V}_{O_2}$?}
	\framesubtitle{None on multivariate analysis. Weak correlation on scatter-plot analysis.}
	\begin{columns}[t]
		\column{0.5\textwidth}
		\begin{figure}
			\includegraphics[width=\textwidth]{../Figures/cpet_oj_scatter_at_bil}
			\\ $\dot{V}_{O_2}$AT versus serum bilirubin
		\end{figure}

		\column{0.5\textwidth}
		\begin{figure}
			\includegraphics[width=\textwidth]{../Figures/cpet_oj_scatter_peak_bil}
			\\ $\dot{V}_{O_2}$Peak versus serum bilirubin
		\end{figure}
	\end{columns}
\end{frame}

\begin{frame}
	\frametitle{Jaundice and other patient characteristics}
	\framesubtitle{What was the relationship between obstructive jaundice and other parameters?}

	\begin{columns}
	\column[c]{0.5\textwidth}

	\begin{figure}
		\includegraphics[width=\textwidth]{jaundice_distribution}
	\end{figure}

	\begin{figure}
		\includegraphics[width=\textwidth]{jaundice_vs_patient_factors}
	\end{figure}

	\column[c]{0.5\textwidth}		
	{\scriptsize			
	Severity of systemic inflammation proportionate to severity of jaundice. \\
	\medskip

@@

	Jaundiced patients were more likely to be anaemic, with lower haematocrit and lower mean corpuscular volume.\\
	\medskip

	No significant difference in the preoperative renal function, prothrombin time and white cell count between jaundiced and non-jaundiced patients.\\
	}

	\end{columns}
\end{frame}

%--CHAPTER 4----CHAPTER 4----CHAPTER 4----CHAPTER 4----CHAPTER 4----CHAPTER 4----CHAPTER 4--
\section[Chapter 4]{CPET and Body Composition}

@@

\section[Chapter 5]{Factors affecting post op inflammation}

@@

\section[Chapter 6]{Postoperative CRP and complications}
\begin{frame}
	\frametitle{Chapter 6}
	\framesubtitle{Postoperative CRP and complications}
	\begin{block}{Title}
		An investigation into the relationship between postoperative systemic inflammation and complications after pancreaticoduodenectomy.
	\end{block}
\end{frame}

@@

\section[Chapter 7]{Discussion}
